---
title: "Maps of seconday data sites"
author: "GGL"
date: "03/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plotting sites of secondary datasets on map (see Excel for details on datasets)

Check to see if packages are installed. Install them if they are not, then load them into the R session.
```{r}
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}

```

Load packages (velox package not loading so removed)
```{r}
# List of packages

packages <- c("tidyverse","reshape2","readxl","foreign",
              "sf","rworldmap","ggplot2","dplyr","tmap",
              "countrycode", "rgdal", "ggrepel")
ipak(packages)
```

# set file paths
```{r}
path_map_shp <- "/Users/georgiagore-langton/OneDrive - London School of Hygiene and Tropical Medicine/PhD_1/Training/Learning R/Mapping in R_MCairns code"

path_data <- "/Users/georgiagore-langton/OneDrive - London School of Hygiene and Tropical Medicine/PhD_1/Data sources"

path_save <- "/Users/georgiagore-langton/OneDrive - London School of Hygiene and Tropical Medicine/PhD_1/Upgrading/Upgrading Report"
```


# import dataset made in Excel with HF coordinates 
```{r}
long_lat <- read_excel(paste(path_data, "20200706_plotting study locations data.xlsx", sep="/"))
```


# generate iso3 code
```{r}
countries <- c(long_lat$Country)
iso3 <- countrycode(countries, origin = 'country.name', destination = 'iso3c')
long_lat$iso3 <- iso3 
```

# Read in shape file Africa country map

```{r}
shp0 <- readOGR(path_map_shp, layer=  "africa_countries_from_admin1")
plot(shp0)
```

# some data managemebt before plotting

```{r}
long_lat <- long_lat %>% group_by(Country) %>% 
    mutate(n=row_number()) %>% 
  ungroup() %>% 
   mutate(study_lab = paste(Study, Year, sep = ", "))

# same study has multiple sites very near each other- they overlap in map - so only plot once for each study in each site

long_lat_plot <- long_lat %>% group_by(Study, Country) %>% 
  mutate(n_cont_study = row_number()) %>% 
  filter(n_cont_study == 1)

```



# convert shape file to dataframe

```{r}
plot <- fortify(shp0)
```


# plot map with study sites marked

```{r}

plot <- ggplot() + geom_path(data = plot, 
          aes(x = long, y = lat, group = group),
          color = 'grey', fill = 'white', size = .2) + coord_map() + 
  geom_point(data = long_lat_plot, aes(x = Long, y = Lat, colour = study_lab), size = 1, alpha = 9/10) +
  geom_text_repel(data=long_lat_plot, aes(x = Long, y = Lat, label=if_else(n==1, Country,""))) +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),plot.background=element_blank()) +
   theme(legend.key=element_blank()) +
   coord_sf(xlim = c(-20, 55), ylim = c(-20,15), expand = FALSE) +
   labs(colour = "Study")

plot + scale_color_brewer(palette = "Set1")

ggsave(paste(path_save, "map_study_locations.pdf", sep="/"))
```




